\documentclass{article}

\include{definitions}

\pagestyle{empty}
\setlength\parindent{0pt}

\begin{document}

\noindent {\huge \textbf{Team:}}\\

\section*{Setting}
Collaboratively decide upon the setting of the game.
\begin{chooseone}
\item A campy version of the late 1960s
\item A campy version of the 1980s
\item A campy version of the present
\end{chooseone}

\section*{Background}
Choose one of the following backgrounds for your
 heroic association.
 \begin{chooseone}
 \item You are a group of friends who formed a pact years ago
   to fight crime together. You know each others' identities
   and backgrounds.
 \item You are an alliance of independent heroes who work
   together to fight for justice. You have a deep respect for each
   others' privacy and secrets.
 \item You are a rag-tag group of youth who fight crime.
 \end{chooseone}


\section*{HQ}
Choose one of the following locations for your headquarters.
\begin{chooseone}
\item A normally-inaccessible portion of a mansion.
\item A secure floor of a downtown skyscraper.
\item An underground bunker hidden in a remote or run-down area.
\end{chooseone}

\section*{Heroes}
Each player chooses a playbook and follows the instructions to
create their hero. Work separately up through the \emph{Bonds}
section, at which point you go around the table to introduce yourselves,
then go around the table again to determine initial Bonds.

\section*{Team Identity}
Finally, work together to name your team and write it above.

Now you are ready for adventure!


\end{document}