\documentclass[letterpaper]{article}
\usepackage{fullpage}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{pifont}
\usepackage{multicol}
\usepackage{titlesec}

\pagestyle{empty}
\setlength\parindent{0pt}

\include{definitions}

\titlespacing*{\subsection}{0pt}{\baselineskip}{0pt}

\newsavebox{\footer}

% Section heading for the creation page
\newcommand{\head}{\subsection*}

% Annotate the moves connected to an attribute
\newcommand{\annotate}[1]{\textit{\small #1}}

% Parameters:
% #1: The name of the playbook.
% #2: Extra creation sections (e.g. Gear)
% #3: Bonds instructions
% #4: Playbook moves
\newenvironment{playbook}[5]
{
  \newcommand{\pbname}{#1}
  \newcommand{\pbblurb}{#2}
  \newcommand{\pbextra}{#3}
  \newcommand{\pbbonds}{#4}
  \newcommand{\pbmoves}{#5}
  
  \newpage

  \begin{multicols}{2}
    [
    \section*{Introducing the \pbname}
    \textit{#2}
    ]

    \head{Heroic Identity}
    Come up with a name for your Hero and describe their heroic
    appearance. Remember, all heroes need a mask to protect their
    secret identities.

    \head{Secret Identity}
    Write down your hero's real name and appearance.
    Leave the occupation blank for now.

    \head{Attributes}
    Choose one attribute to have a +2 and another to have +1.
    Then, either set the other two at 0 or, if you prefer, set one
    at +1 and one at -1.

    Your Endurance is equal to your Mighty +4. Draw that many
    empty boxes on your character sheet and mark each of the final
    two with ``-1''.

    \head{Moves}
    Choose two of the \pbname{} Moves in your playbook. You have these
    in addition to all the basic and special moves.

    \pbextra{}
    
    \head{Contact}
    Create one Contact and answer the following questions about them.
    \begin{choices}
    \item Do they know you as a hero, as your secret identity, or both?
      If both, do they know that you are the same person?
    \item How do you know each other?
    \item Why do they trust you?
    \end{choices}
    Write a +2 next to this contact. This is their
    \textit{reliability}---your bonus to exhort them to act.
    
    \head{Bonds}
    All players introduce their heroes by name and look.
    Write down each hero's name under Bonds in your playbook.

    Then, go around again to establish initial Bonds.

    \pbbonds{}

    On others' turns, answer their questions as you like.

    \head{Improvement}
    Whenever you fail a roll or reset your Bond with another hero,
    mark one Experience. When you mark your fifth Experience,
    do one of the following, but you can choose each only once.
    \begin{chooseone}
    \item Add +1 Mighty
    \item Add +1 Focused
    \item Add +1 Intellectual
    \item Add +1 Savvy
    \item Add +1 Endurance
    \item Choose another \pbname{} move
    \end{chooseone}
    
    
  \end{multicols}

 
  % Savebox allows us to use the variable in the enddef, as shown
  % in http://joshua.smcvt.edu/latex2e/_005cnewenvironment-_0026-_005crenewenvironment.html
  \sbox\footer{\large \textit{\uppercase{#1}}}

  \newpage
  
  \begin{minipage}{0.6\textwidth}
  {\Large Name:} \bigskip\\
  {\Large Heroic Appearance:}\\
  \end{minipage}
  \begin{minipage}{0.4\textwidth}
    Real Name:\\
    Occupation:\\
    Unmasked Appearance:\\
  \end{minipage}
  \bigskip


  \setlength{\columnsep}{1cm}
  \begin{minipage}{0.5\textwidth}
  \begin{tabular}{lll}
    \large{Mighty}
      & \framebox[0.25in]{\strut}
      & \annotate{Rumble, Heroic Feat} \\
    \large{Focused}
      & \framebox[0.25in]{\strut}
      & \annotate{Prowl, Race/Chase} \\
    \large{Intellectual}
      & \framebox[0.25in]{\strut}
      & \annotate{Investigate} \\
    \large{Savvy}
      & \framebox[0.25in]{\strut}
      & \annotate{Exhort, Scrutinize} \\
  \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\textwidth}
    \large{Forward:} \hspace{2cm}  \large{Hold:}\\
    
    \large{Experience:}
    \framebox[0.25in]{\strut}
    \framebox[0.25in]{\strut}
    \framebox[0.25in]{\strut}
    \framebox[0.25in]{\strut}
    \framebox[0.25in]{\strut}\\
    
    \noindent \large{Endurance:}\\
  \end{minipage}
  \medskip

  \begin{multicols}{2}
  \begin{minipage}{0.5\textwidth}
  {\large \pbname{} Moves:}
  \pbmoves{}
  \end{minipage}
  \bigskip

  \begin{minipage}{0.5\textwidth}
  {\large Contacts:}
  \vspace{3cm}
  \end{minipage}

  \begin{minipage}{0.5\textwidth}
  \noindent {\large Bonds: \annotate{Help/Hinder}}
  \vspace{3cm}
  \end{minipage}

  \begin{minipage}{0.5\textwidth}
  \noindent {\large Gear:}
  \vspace{3cm}
  \end{minipage}
  
  \end{multicols}
}
{
   \vfill
   \hfill{} \usebox{\footer}
}

\newenvironment{playbookmoves}
{\begin{itemize}[label=\ding{109}]}
{\end{itemize}}

\newcommand{\comm}{You have a two-way radio for communicating with the
  rest of your team.}

\begin{document}

\begin{playbook}{Daredevil}
{
  Agile and fearless, leaping into danger, always willing to
  risk their own safety to save another.
}
{
  \head{Gear}
  \comm{}

  You may also choose one of the following:
  \begin{chooseone}
  \item A signature blunt weapon (+1 brawl)
  \item A signature thrown blunt weapon (inflict Endurance damage on heroic feat)
  \end{chooseone}
}
{
  On your turn, ask any of the following:
  \begin{choices}
  \item \textit{Which of you impressed me with your bravery?}
    For those characters, write Bond +2.
  \item \textit{Which of you strikes me as unreliable?}
    For those characters, write Bond -1.
  \end{choices}

  For everyone else, write Bond +1. They have seen what you can do,
  and they are impressed.
}
{
  \begin{playbookmoves}
  \item \move{Precise strikes}: When you rumble, roll+Focused instead.
  \item \move{Escape artist}: When you escape bondage, roll+Focused. On a 10+,
    you Silently escape from your bonds. On a 7--9, you escape from your
    bonds and choose one of the following.
    \begin{choices}
    \item An ally is placed in danger.
    \item Your escape is detected.
    \end{choices}
    \onamiss{}
  \item \move{Parkour}: When you run through otherwise impassable
    obstacles, roll+Focused.  On a 10+, you successfully maneuver
    through. On a 7--9, you maneuver through but must choose one of the
    following.
    \begin{choices}
    \item Lose Endurance.
    \item An ally is placed in danger.
    \end{choices}
    \onamiss{}
  \end{playbookmoves}
}
\end{playbook}

\begin{playbook}{Enigma}
{
  A mystery even to their own allies.
}    
{
  \head{Gear}
  Choose one of the following:
  \begin{chooseone}
  \item A two-radio for communicating with the rest of the team.
  \item Smoke bombs: +1 to Appear Fortuitously and Disappear Mysteriously when used.
  \item Gas gun: Gain the option to knock out a lackey in a rumble.
  \end{chooseone}
  
  \head{Secrets}
  Regardless of what was chosen for the Team sheet, you
  neither live with nor share a HQ with the rest of them,
  nor do any of them know your secret identity.
  Instead, your HQ is a hidden room in your home or apartment.
  Answer the following questions:
  \begin{choices}
  \item Why is it important that you keep your identity secret?
  \item Who knows the location of your HQ, if anyone?
  \end{choices}
}
{
  On your turn, ask any of the following.
  \begin{choices}
  \item \textit{Whose secret identity do I know?}
    For those characters, write Bond +2.
  \item \textit{Who attempted to discover my identity against my will?}
    for those characters, write Bond -2.
  \end{choices}
  For everyone else, write Bond +1. Even though they do not know you,
  they have seen that they can trust you.
}
{
  \begin{playbookmoves}
  \item \move{Appear fortuitously}: When you enter a scene in progress,
    roll+Intellectual. On a 10+, take +2 forward. On a 7--9, choose one.
    \begin{choices}
    \item The entrance is disorienting; take -1 forward.
    \item Place an ally or innocent in danger.
    \end{choices}
    \onamiss{}
  \item \move{Disappear mysteriously}: When you attempt to escape
    danger from a scene in progress, roll+focused. On a 10+, you leave
    the scene and dissipate any danger you were in. On a 7--9, you
    leave the scene, but a friendly character in the scene is
    endangered. \onamiss{}
  \item \move{Power of the unknown}: When you exhort an NPC to do something,
    add Savvy.
  \end{playbookmoves}
}
\end{playbook}

\begin{playbook}{Face}
{
  Front and center, leading the team in the fight for justice.
}
{
  \head{Gear}
  \comm{}
  Additionally, choose one of the following.
  \begin{chooseone}
  \item Team Symbol: +2 to exhort a friendly NPC when used.
  \item Shield: +2 to help allies in a rumble.
  \end{chooseone}
}
{
  On your turn, ask any of the following:
  \begin{choices}
  \item \textit{Who proved their loyalty to me in a stressful situation?}
    For those characters, write Bond +3.
    
  \item \textit{Who served under my management or command in other circumstances?}
    For those characters, write Bond +2.
  \end{choices}

  For everyone else, write Bond +1. The group knows you would not
  lead them astray.
}
{
  \begin{playbookmoves}
  \item \move{Leadership}: When you \move{help} an ally, add Savvy
    and they take +1 forward.
  \item \move{Inspiring}: When you exhort, add +1.
  \item \move{Orator}: When you deliver a heroic monologue,
    roll+Savvy. On a 10+, all present allies take +2 forward. On a
    7--9, all present allies take +1 forward.  \onamiss{}
  \end{playbookmoves}
}
\end{playbook}

\begin{playbook}{Sleuth}
{
  Someone has a problem? You can find the answers.
}    
{
  \head{Gear}
  \comm{}
  Additionally, choose one of the following.
  \begin{chooseone}
  \item Concealing trenchcoat: +1 to prowl and stake out.
  \item Notebook: +1 to scrutinize.
  \end{chooseone}
}
{
  On your turn, ask any of the following:
  \begin{choices}
  \item \textit{Which of you do I know something secret about?}
    For those characters, write Bond +2.
  \item \textit{Which of you know something secret about me?}
    For those characters, write Bond +1.
  \end{choices}
  
  For everyone else, write Bond 0. Your uncanny insight into people
  and their motivations can sometimes put your teammates on edge.
}
{
  \begin{playbookmoves}
  \item \move{Stake Out}: When you stake out a location, roll+Focused. On a 10+, choose 3. On a 7--9, choose 1.
    \begin{choices}
    \item Your target arrives at or is discovered at your stakeout.
    \item Discover a fact about the defenses of the location.
    \item Reveal a pattern that you can exploit later (hold, +2 when exploited)
    \item Prevent your stakeout from being discovered.
    \end{choices}
    \onamiss{}
  \item \move{Street Smarts}: When you investigate, add Savvy.
  \item \move{Not born yesterday}: When you scrutinize, add Intellectual.
  \end{playbookmoves}
}
\end{playbook}

\begin{playbook}{Technologist}
{
  Has the tools and the know-how to get the job done.
}
{
  \head{Gear}
  \comm{}
  You are known for carrying useful gear on your adventures;
  choose how you would carry such gear.
  \begin{chooseone}
  \item Pocketed coat
  \item Utility belt
  \item Satchel
  \item Backpack
  \end{chooseone}
}
{
  On your turn, ask any of the following.
  \begin{choices}
  \item \textit{Which of you shares a passion for technology?}
    For those characters, write Bond +2
  \item \textit{Which of you were endangered because of one of my gadgets?}
    For those characters, write Bond +1.
  \end{choices}
  For everyone else, write Bond 0. You spend so much time with your
  gadgets and computers that your relationship with your teammates
  is not as strong as it could be.
}
{
  \begin{playbookmoves}
  \item \move{Gadgeteer}: When you declare what gadget you have brought and how you wish to use it, then roll+Intellectual. On a 10+, the gadget proves useful toward your desired end. On a 7--9, choose one:
    \begin{choices}
      \item Place an ally or innocent in danger
      \item Lose one Endurance
      \end{choices}
      \onamiss{}
    \item \move{Supercomputer}:
      Choose the location of your supercomputer:
      \begin{chooseone}
      \item Your home
      \item Your HQ
      \item Your place of employment
      \end{chooseone}
      Add to your Gear a remote terminal to your supercomputer.
      When you investigate and have access to your supercomputer, add +2. 
    \item \move{Hacker}: When you hack a system, roll+Intellectual. On a
      10+, choose~3. On a 7--9, choose~1.
      \begin{choices}
      \item Disable a system or device.
      \item Observe or gather data on a distant or hidden area.
      \item Discover a fact about a threat, system, or organization.
      \item Prevent another character from accessing or using the system.
      \item Find the location of a person or thing.
      \item Prevent the hack from being discovered.
      \end{choices}
      \onamiss{}
  \end{playbookmoves}
}
\end{playbook}

\begin{playbook}{Tough}
{
  When it gets down to brass tacks, the team is going to need some muscle.
}    
{
  \head{Gear}
  \comm{}
  Additionally choose one of the following.
  \begin{chooseone}
  \item Iconic weapon: +1 rumble when wielding.
  \item Armored suit: Automatically reduce Endurance loss by one
    when you take a hit.
  \end{chooseone}

  \head{Training}
  Choose the training background.
  \begin{chooseone}
  \item Martial arts 
  \item Boxing
  \item Wrestling
  \end{chooseone}

  Name your \textit{Special Move} based on your selection.
}
{
  On your turn, ask any of the following:
  \begin{choices}
  \item \textit{Which of you saved me from danger when I got in over my head?}
    For those characters, write Bond +3.
  \item \textit{Which of you are training to improve your physique and willpower?} For those characters, write Bond +2.
  \end{choices}
  For everyone else, write Bond +1. You've got their backs.
}
{
  \begin{playbookmoves}
  \item \move{Endurance Training}: Add mighty to your Endurance again.
  \item \move{Second Wind}: When you get your second wind,
    roll+Mighty. On a 10+, recover all Endurance. On a 7--9, recover
    two Endurance, up to your maximum. \onamiss{}
  \item \move{Iron Will}: You may ignore the penalties from being imperiled.
    Remove the ``-1'' markers from your Endurance boxes.
  \item \move{Special Move}: When you rumble, you have the following
    additional option.
    \begin{choices}
    \item Incapacitate your enemy with your special move.
    \end{choices}
  \end{playbookmoves}
}
\end{playbook}

\end{document}